The Lipid Interactome Repository

### 2025-07-29 index.qmd
I tried cleaning things up and it made a lot of changes... Hoping this will push properly.

---
title: "The Lipid Interactome Repository"
format: 
  html:
    embed-resources: false
standalone: false
---

@@

<!-- **This repository is still under construction, please forgive us for incomplete sections as we build features!** -->

@@

  <a href="LipidProbe/Phosphatidylalcohol.qmd" style="text-decoration: none;">
      <button style="background-color:rgb(41, 204, 131); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
          Phosphatidyl Alcohol
      </button>
  </a>

>>>>

---
title: "The Lipid Interactome Repository"
format: 
  html:
    template-engine: jinja
    embed-resources: false

standalone: false
---

@@

@@

  <a href="LipidProbe/Phosphatidylalcohol.qmd" style="text-decoration: none;">
      <button style="background-color:rgba(41, 204, 131, 1); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
          Phosphatidyl Alcohol
      </button>
  </a>
